% DOCUMENT FORMATING
\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}

% PACKAGES
\usepackage{amsmath} % For extended formatting
\usepackage{amssymb} % For math symbols
\usepackage{amsthm} % For proof environment
\usepackage{array} % For tables
\usepackage{enumerate} % For lists
\usepackage{extramarks} % For headers and footers
\usepackage{fancyhdr} % For custom headers
\usepackage{graphicx} % For inserting images
\usepackage{multicol} % For multiple columns
\usepackage{verbatim} % For displaying code
\usepackage{tkz-euclide}
\usepackage{pgfplots}
\usepackage{graphicx}

% SET UP HEADER AND FOOTER
\pagestyle{fancy}
\lhead{\MyCourse} % Top left header
\chead{\MyTopicTitle} % Top center header
\rhead{\MyAssignment} % Top right header
\lfoot{\MyCampus} % Bottom left footer
\cfoot{} % Bottom center footer
\rfoot{\MySemester} % Bottom right footer
\renewcommand\headrulewidth{0.4pt} % Size of the header rule
\renewcommand\footrulewidth{0.4pt} % Size of the footer rule
% ----------
% TITLES AND NAMES 
% ----------

\newcommand{\MyCourse}{Math 241}
\newcommand{\MyTopicTitle}{Application of Derivative Practice}
\newcommand{\MyAssignment}{Name: \qquad \qquad \qquad}
\newcommand{\MySemester}{Fall 2019}
\newcommand{\MyCampus}{University of Hawaii at Manoa}

% ----------
% BEGIN DOCUMENT
% ----------

\begin{document}
\textbf{Direction} Read each question and evaluate the answers. Try doing your work on a seperate piece of paper.
\begin{enumerate}
    \item A spherical balloon is being inflated. What is the volume of the sphere at the instant when the rate of increase of the surface area is four times the rate of increase of the radius of the sphere? 
    \item A camera on the ground is 100 m away from a model rocket launch pad. When the rocket is launched, it rises at a constant velocity if 20 m/s. How fast must the camera's angle change when the rocket is 100 m high?
    \item You have 500 ft of fence to enclose your children in a rectangular area. What are the dimensions of the fence that will give you the maximum area?
    \item Find the most general antiderivatives of the following functions: a)f'(x) = $x^{4}-3x^{2}+1$ b) g'(x) = $5\sec(x)2\tan(x)$ c) h'(x) =  $(x)(x-3)^{2}$ d) z'(x) = $(x)(x-5)(x-2)$
    \item If z is a differentiable function and z(5) = 10 and z'(5) = 2, what is the approximate value of z(5.5)? \newline 
    \item What is the approximate value of $\cos{62^{\circ}}$?
    \item Find the critical point(s) of the function f(x) = $4x^{2} - 3x + 2$.
    \item Given the cost function C(x) = $500x + 6x + 0.2x^{2}$ and the revenue function R(x) = 20x, how many units should be produced to have the maximum profit?
    \textbf{HINT} Profit can be found by using R(x) - C(x) \newline  
    \item A plane lifts off from a runway at an angle of 30 degrees. If the speed of the plane is 500 $\frac{mi}{hr}$, then how fast is the plane gaining altitude? 
    \item Find two positive numbers that add up to 30 such that the maximum product is possible. 
    \item Using Newton's Method, determine $x_{2}$ for f(x) = x$\cos(x)$-$x^{2}$ if $x_{0}$ = 1.
    \item Find the local maximum, local minimum, absolute maximum, absolute minimum, \& inflection point(s) of the following function f(x) = $\frac{x^{2}+4}{8x}$
\end{enumerate}

\end{document}